---
title: "Negative Binomial Regression (user-level)"
author: "yijing"
date: "2024-07-09"
output: html_document
---

# Generating Negative Binomial regression output for user-level analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(svyVGAM)
library(survey)
library(pscl)
library(ggplot2)
library(MASS)
library(performance)
library(tidyverse)
library(AER)
library(dotwhisker)
library(glmmTMB)

ROOTPATH <- substr(getwd(), 1, nchar(getwd())-12)
ROOTPATH
```

## Load data

```{r}
reg_table <- read.csv(paste(ROOTPATH, "output/reg_table_filter_ytb_activities_122324.csv", sep=""))
reg_table$age = reg_table$age / 10
reg_table$timespan_imputed = reg_table$timespan_imputed / 60
reg_table
```

## Negative Bionomial regression (NBR) - using glmmTMB

### NBR with Anti-/Pro-gov 

Here we use the same code template and tweak a few parameters to produce 4 figures 

- Figure 3 (main text): include `if_progov`, `if_antigov` in the IVs; keeping respondents who have engaged with any youtube content in a certain form (Table 3)
- Figure 10-A (appendix): include `extreme_antiPro` in the IVs; keeping respondents who have engaged with any youtube content in a certain form (Table 3)
- Figure 14-A1 (appendix): include `if_progov`, `if_antigov` in the IVs; keeping all respondents who have and have not engaged with youtube content (N = 735)
- Figure 14-B1 (appendix): include `extreme_antiPro` in the IVs; keeping all respondents who have and have not engaged with youtube content (N = 735)
  
- produce Figure 
```{r}
# 1: build models
nbr.view <- glmmTMB(
  view_counts ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 3, Figure 14-A1
  #view_counts ~ gender + age + education + timespan_imputed + interest_politics + extreme_antiPro,  # Figure 10-A, Figure 14-B1
  weights = weight,
  data = reg_table,  # Figure 14-A1, Figure 14-B1
  #data = subset(reg_table, if_view==1),  # Figure 3, Figure 10-A
  family = nbinom2)

nbr.subscribe <- glmmTMB(
  subscribe_counts ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 3, Figure 14-A1
  #subscribe_counts ~ gender + age + education + timespan_imputed + interest_politics + extreme_antiPro,  # Figure 10-A, Figure 14-B1
  weights = weight,
  data = reg_table,  # Figure 14-A1, Figure 14-B1
  #data = subset(reg_table, if_subscribe==1),  # Figure 3, Figure 10-A
  family = nbinom2)

nbr.comment <- glmmTMB(
  comment_counts ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 3, Figure 14-A1
  #comment_counts ~ gender + age + education + timespan_imputed + interest_politics + extreme_antiPro,  # Figure 10-A, Figure 14-B1
  weights = weight,
  data = reg_table,  # Figure 14-A1, Figure 14-B1
  #data = subset(reg_table, if_comment==1),   # Figure 3, Figure 10-A
  family = nbinom2)

# 2. show model summary: uncomment this block for more details on the NBR results
#summary(nbr.view)
#summary(nbr.subscribe)
#summary(nbr.comment)

# 3: visualize results
models <- list(comment=nbr.comment, subscribe=nbr.subscribe, view=nbr.view)
reg_plot = dwplot(models, 
                  dot_args=list(size=5), 
                  whisker_args=list(size=1.5)) +
    #facet_grid(~model, scales="free_x") + # if allowing for flexible scaling
    facet_grid(~model) +
    theme_bw(base_size = 10) +
    geom_vline(xintercept = 0, colour = "black", linetype = 2, size=1) + 
    scale_color_manual(values=c("#4582b4", "#ff4500","#2d8b57")) + 
    theme(legend.position="none") + 
    #ggtitle("(B)") + 
    theme(
      plot.title = element_text(face = "bold", size=24),
      text = element_text(size = 22),
      axis.text.x = element_text(size=15)) + 
    scale_y_discrete(labels = c("anti-gov", "pro-gov", "interest in politics", "timespan", "education", "age","gender"))  # Figure 3, Figure 14-A1
    #scale_y_discrete(labels = c("anti-/pro-gov\nextremity", "interest in politics", "timespan", "education", "age","gender"))  # Figure 10-A, Figure 14-B1

# 4: save figures: uncomment this block to save the output figures
#ggsave(
  #paste(ROOTPATH, "output/results-summary-051425/nbr_coeff_nbinom2_antipro.pdf", sep=""), 
  #device="pdf",
  #width=10,
  #plot=reg_plot)

reg_plot
```

### NBR with left/right

Here we use the same code template and tweak a few parameters to produce 4 figures 

- Figure 9: include `if_left`, `if_right` in the IVs; keeping respondents who have engaged with any youtube content in a certain form (Table 3)
- Figure 10-B (appendix): include `extreme_lftRght` in the IVs; keeping respondents who have engaged with any youtube content in a certain form (Table 3)
- Figure 14-A2 (appendix): include `if_left`, `if_right` in the IVs; keeping all respondents who have and have not engaged with youtube content (N = 735)
- Figure 14-B2 (appendix): include `extreme_lftRght` in the IVs; keeping all respondents who have and have not engaged with youtube content (N = 735)

```{r}
# 1: build models
nbr.view <- glmmTMB(
  view_counts ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 9, Figure 14-A2
  #view_counts ~ gender + age + education + timespan_imputed + interest_politics + extreme_lftRght,  # Figure 10-B, Figure 14-B2
  weights = weight,
  data = reg_table,  # Figure 14-A2, Figure 14-B2
  #data = subset(reg_table, if_view==1),  # Figure 9, Figure 10-B
  family = nbinom2)

nbr.subscribe <- glmmTMB(
  subscribe_counts ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 9, Figure 14-A2
  #subscribe_counts ~ gender + age + education + timespan_imputed + interest_politics + extreme_lftRght,  # Figure 10-B, Figure 14-B2
  weights = weight,
  data = reg_table,  # Figure 14-A2, Figure 14-B2
  #data = subset(reg_table, if_subscribe==1),  # Figure 9, Figure 10-B
  family = nbinom2)

nbr.comment <- glmmTMB(
  comment_counts ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 9, Figure 14-A2
  #comment_counts ~ gender + age + education + timespan_imputed + interest_politics + extreme_lftRght,  # Figure 10-B, Figure 14-B2
  weights = weight,
  data = reg_table,  # Figure 14-A2, Figure 14-B2
  #data = subset(reg_table, if_comment==1),  # Figure 9, Figure 10-B
  family = nbinom2)

# 2. show model summary: uncomment this block for more details on the NBR results
#summary(nbr.view)
#summary(nbr.subscribe)
#summary(nbr.comment)

# 3: visualize results
models <- list(comment=nbr.comment, subscribe=nbr.subscribe, view=nbr.view)
reg_plot = dwplot(models, 
                  dot_args=list(size=5), 
                  whisker_args=list(size=1.5)) +
    facet_grid(~model, scales="free_x") +  # if allowing for flexible scaling
    facet_grid(~model) +
    theme_bw(base_size = 10) +
    geom_vline(xintercept = 0, colour = "black", linetype = 2, size=1) + 
    scale_color_manual(values=c("#4582b4", "#ff4500","#2d8b57")) + 
    theme(legend.position="none") + 
    #ggtitle("(B)") +
    theme(
      plot.title = element_text(face = "bold", size=24),
      text = element_text(size = 22),
      axis.text.x = element_text(size=15)) + 
    scale_y_discrete(labels = c("right", "left", "interest in politics", "timespan", "education", "age","gender"))  # Figure 9, Figure 14-A2
    #scale_y_discrete(labels = c("left/right\nextremity", "interest in politics", "timespan", "education", "age","gender"))  # Figure 10-B, Figure 14-B2

# 4: save figures: uncomment this block to save the output figures
#ggsave(
  #paste(ROOTPATH, "output/results-summary-051425/nbr_coeff_nbinom2_antipro.pdf", sep=""), 
  #device="pdf",
  #width=10,
  #plot=reg_plot)

reg_plot
```
















