---
title: "Negative Binomial Regression (user-level) with channel category breakdown"
author: "yijing"
date: "2024-07-09"
output: html_document
---

# Generating Negative Binomial regression output for user-level analysis (with breakdowns for different channel categories)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(svyVGAM)
library(survey)
library(pscl)
library(ggplot2)
library(MASS)
library(performance)
library(tidyverse)
library(AER)
library(dotwhisker)
library(glmmTMB)

ROOTPATH <- substr(getwd(), 1, nchar(getwd())-12)
ROOTPATH
```

## Load data

```{r}
reg_table <- read.csv(paste(ROOTPATH, "output/reg_table_filter_ytb_activities_channel_catg_counts_122324.csv", sep=""))
reg_table$age = reg_table$age / 10
reg_table$timespan_imputed = reg_table$timespan_imputed / 60
reg_table
```

## Negative Bionomial regression (NBR) - using glmmTMB

### NBR with Anti-/Pro-gov 

Here we use the same code template and tweak a few parameters to produce 3 figures 

- Figure 12-A: using count of views/subscribes/comments under the anti-government channels as DVs
- Figure 12-B: using count of views/subscribes/comments under the neutral channels as DVs
- Figure 12-C: using count of views/subscribes/comments under the pro-government channels as DVs

```{r}
# 1: build models
nbr.view <- glmmTMB(
  #view_anti ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-A
  #view_netr ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-B
  view_pro ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-C
  weights = weight,
  data = subset(reg_table, if_view==1), 
  family = nbinom2)

nbr.subscribe <- glmmTMB(
  #subscribe_anti ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-A
  #subscribe_netr ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-B
  subscribe_pro ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-C
  weights = weight,
  data = subset(reg_table, if_subscribe==1), 
  family = nbinom2)

nbr.comment <- glmmTMB(
  #comment_anti ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-A
  #comment_netr ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-B
  comment_pro ~ gender + age + education + timespan_imputed + interest_politics + if_progov + if_antigov,  # Figure 12-C
  weights = weight,
  data = subset(reg_table, if_comment==1), 
  family = nbinom2)

# 2. show model summary: uncomment this block for more details on the NBR results
#summary(nbr.view)
#summary(nbr.subscribe)
#summary(nbr.comment)

# 3: visualize results
models <- list(comment=nbr.comment, subscribe=nbr.subscribe, view=nbr.view)
reg_plot = dwplot(models, 
                  dot_args=list(size=5), 
                  whisker_args=list(size=1.5)) +
    facet_grid(~model, scales="free_x") +
    theme_bw(base_size = 10) +
    geom_vline(xintercept = 0, colour = "black", linetype = 2, size=1) + 
    scale_color_manual(values=c("#4582b4", "#ff4500","#2d8b57")) + 
    theme(legend.position="none") + 
    #ggtitle("(A) Anti-government channels") +   # Figure 12-A
    #ggtitle("(B) Neutral channels") +  # Figure 12-B
    ggtitle("(C) Pro-government channels") +  # Figure 12-C
    theme(
      plot.title = element_text(face = "bold", size=24),
      text = element_text(size = 22),
      axis.text.x = element_text(size=15)) + 
    scale_y_discrete(labels = c("anti-gov", "pro-gov", "interest in politics", "timespan", "education", "age","gender"))
  
# 4: save figures: uncomment this block to save the output figures
#ggsave(
  #paste(ROOTPATH, "output/results-summary-122724/nbr_coeff_nbinom2_progov_channels_lftrght.pdf", sep=""), 
  #device="pdf",
  #width=10,
  #plot=reg_plot)
reg_plot
```


### NBR with Left/right

Here we use the same code template and tweak a few parameters to produce 3 figures 

- Figure 13-A: using count of views/subscribes/comments under the anti-government channels as DVs
- Figure 13-B: using count of views/subscribes/comments under the neutral channels as DVs
- Figure 13-C: using count of views/subscribes/comments under the pro-government channels as DVs

```{r}
# 1: build models
nbr.view <- glmmTMB(
  view_anti ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-A
  #view_netr ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-B
  #view_pro ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-C
  weights = weight,
  data = subset(reg_table, if_view==1), 
  family = nbinom2)

nbr.subscribe <- glmmTMB(
  subscribe_anti ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-A
  #subscribe_netr ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-B
  #subscribe_pro ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-C
  weights = weight,
  data = subset(reg_table, if_subscribe==1), 
  family = nbinom2)

nbr.comment <- glmmTMB(
  comment_anti ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-A
  #comment_netr ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-B
  #comment_pro ~ gender + age + education + timespan_imputed + interest_politics + if_left + if_right,  # Figure 13-C
  weights = weight,
  data = subset(reg_table, if_comment==1), 
  family = nbinom2)

# 2. show model summary: uncomment this block for more details on the NBR results
#summary(nbr.view)
#summary(nbr.subscribe)
#summary(nbr.comment)

# 3: visualize results
models <- list(comment=nbr.comment, subscribe=nbr.subscribe, view=nbr.view)
reg_plot = dwplot(models, 
                  dot_args=list(size=5), 
                  whisker_args=list(size=1.5)) +
    facet_grid(~model, scales="free_x") +
    theme_bw(base_size = 10) +
    geom_vline(xintercept = 0, colour = "black", linetype = 2, size=1) + 
    scale_color_manual(values=c("#4582b4", "#ff4500","#2d8b57")) + 
    theme(legend.position="none") + 
    ggtitle("(A) Anti-government channels") +   # Figure 13-A
    #ggtitle("(B) Neutral channels") +  # Figure 13-B
    #ggtitle("(C) Pro-government channels") +  # Figure 13-C
    theme(
      plot.title = element_text(face = "bold", size=24),
      text = element_text(size = 22),
      axis.text.x = element_text(size=15)) + 
    scale_y_discrete(labels = c("right", "left", "interest in politics", "timespan", "education", "age","gender"))
  
# 4: save figures: uncomment this block to save the output figures
#ggsave(
  #paste(ROOTPATH, "output/results-summary-122724/nbr_coeff_nbinom2_progov_channels_lftrght.pdf", sep=""), 
  #device="pdf",
  #width=10,
  #plot=reg_plot)
reg_plot
```
