---
title: "Supplementary analysis for user-level analysis"
author: "written by Zoltan, cleaned by Yijing"
date: "2024-07-09"
output: html_document
---

# Supplementary analysis at the user level

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(lubridate)
library(dplyr)
library(sjmisc)
library(sjPlot)
library(sjstats)
library(sjlabelled)
library(lme4)
library(lmerTest)
library(ggplot2)
library(lavaan)
library(psych)
library(mice)
library(miceadds)
library(broom.mixed)
library(margins)
library(readr)

ROOTPATH <- substr(getwd(), 1, nchar(getwd())-12)
ROOTPATH
```

## Marginal prediction - Figure 11

joint effect of political interest and anti/pro-gov scale on the number of viewed political videos


```{r}
data <- read.csv(paste(ROOTPATH, "output/reg_table_filter_ytb_activities_122324.csv", sep=""))

data$polintrest_govsymp=10
data$polintrest_govsymp[data$if_antigov==1] <- 20
data$polintrest_govsymp[data$if_progov==1] <- 30
data$timespan = data$timespan_imputed / 60
data$age = data$age / 10

data$interest_politics[is.na(data$interest_politics)] <- 2
data$polintrest_govsymp[data$interest_politics>=3] <- data$polintrest_govsymp[data$interest_politics>=3]+1

data$polintrest_govsymp <- sjmisc::rec(data$polintrest_govsymp, rec="10=1 [Low PI - Centre];
                                             11=2 [High PI - Centre];
                                             20=3 [Low PI - AntiGov];
                                             21=4 [High PI - AntiGov];
                                             30=5 [Low PI - ProGov];
                                             31=6 [High PI - ProGov]")

data$polintrest_govsymp <- as_factor(data$polintrest_govsymp)

# NB model
pm1 <- data %>%
  filter(if_view==1) %>%
  glm.nb(view_counts ~ gender + age + education +polintrest_govsymp + timespan, 
         data=., weight=weight)  %>%
  plot_model(type="pred")

# plot figure
pm1$polintrest_govsymp +
  xlab("") +
  ylab("") +
  ggtitle("") +
  theme(axis.text=element_text(size=12)) + 
  theme_minimal()

# uncomment this to save figure
#ggsave("polint2.png")
```

## Multiple imputation - Figure 15

Pooled regression results for multiple imputation displaying Average Marginal Effects (AME). 

```{r}
# load data
load(paste(ROOTPATH, "data/TK_DataDonation_eng.Rdata", sep=""))
data <- TK_DataDonation %>%
  dplyr::select(respondent_id, P14_1, P15_1) %>%
  left_join(data, .)

rm(TK_DataDonation)

# create a file for imputtaion
data2 <- data %>%
  dplyr::select(respondent_id, weight, if_view,if_subscribe,if_comment, view_counts,subscribe_counts, comment_counts,
                gender, age, education, interest_politics, P14_1, P15_1, timespan)

data2$GovSymp <- as_factor(rec(data2$P14_1, rec="0:2=1 [AntiGov]; 3:7=2 [Centre]; 8:10=3 [ProGov]; 99=NA"))
data2$LR <- as_factor(rec(data2$P15_1, rec="1:2=1 [Left]; 3:5=2 [Centre]; 6:7=3 [Right]; 9=NA"))

data2 <- dplyr::select(data2, -c("P14_1", "P15_1"))

## impute missing data
b1 <- c("respondent_id", "weight", "if_view","if_subscribe","if_comment", "view_counts", 
        "subscribe_counts", "comment_counts")
b2 <- c("gender","age","education","interest_politics",
        "timespan", "GovSymp","LR")

imp.block.list <- list()
imp.block.list[[1]] <- b1
imp.block.list[[2]] <- b2

p.matrix <- matrix(0,2,15)
p.matrix[2,9:15] <- 1

data.mice <- mice(data2[, c(b1,b2)], m=5, maxit=50,
                  meth='pmm', seed=500, blocks=imp.block.list, predictorMatrix=p.matrix, print = F)
data.comp <- complete(data.mice, action = "long", include = T)

rm(data.mice)
rm(imp.block.list)
rm(p.matrix)
rm(b1, b2)

# solve the factor level issue
data.comp$GovSymp <- data.comp$GovSymp %>%  factor(., levels=c("2","1","3")) %>%
  set_labels(data.comp$GovSymp, labels = c("AntiGov","Centre","ProGov"))

data.comp$LR <- data.comp$LR %>%  factor(., levels=c("2","1","3")) %>%
  set_labels(data.comp$LR, labels = c("Left","Centre","Right"))

data.comp.mids <- as.mids(data.comp)
```

## AME with pro-/anti-gov as IVs

```{r}
# comment
data.comp.comment <- filter(data.comp, if_comment==1)
data.comp.comment.mids <- as.mids(data.comp.comment)
pooled_comment <- with(data.comp.comment.mids, glm.nb(comment_counts ~ gender + age + education + interest_politics +GovSymp  + timespan, 
                                                      weight=weight))

## calculate AME for plot
for (i in 1:5)
{ 
  m_marginal <- glm.nb(comment_counts ~ gender + age + education + interest_politics +GovSymp  + timespan, 
                       weight=weight, data=data.comp.comment, subset=.imp==i)
  if (i==1)
  { 
    save_terms <- tibble(term=names(summary(margins(m_marginal))$AME))
    res_ame <- save_terms 
    res_se <- res_ame
    res_p <- res_ame
  }
  
  res_ame <- bind_cols(res_ame, as_tibble(summary(margins(m_marginal))$AME))
  res_se <- bind_cols(res_se, as_tibble(summary(margins(m_marginal))$SE))
  res_p <- bind_cols(res_p, as_tibble(summary(margins(m_marginal))$p))
}

comment_model <- tibble(term=res_ame$term)
comment_model$ame <- apply(res_ame[,2:6],1, mean)
comment_model$se <- apply(res_se[,2:6],1, mean)
comment_model$p <- apply(res_p[,2:6],1, mean)

comment_model <- summary(pool(pooled_comment)) %>%
  dplyr::select(term, estimate, std.error, p.value) %>%
  left_join(., comment_model)


# subscription
data.comp.subc <- filter(data.comp, if_subscribe==1)
data.comp.subc.mids <- as.mids(data.comp.subc)
pooled_subscr <- with(data.comp.subc.mids, glm.nb(subscribe_counts ~ gender + age + education + interest_politics +GovSymp  + timespan, 
                                                  weight=weight))

## calculate AME for plot
for (i in 1:5)
{ 
  m_marginal <- glm.nb(subscribe_counts ~ gender + age + education + interest_politics +GovSymp  + timespan, 
                       weight=weight, data=data.comp.subc, subset=.imp==i)
  if (i==1)
  { 
    save_terms <- tibble(term=names(summary(margins(m_marginal))$AME))
    res_ame <- save_terms 
    res_se <- res_ame
    res_p <- res_ame
  }
  
  res_ame <- bind_cols(res_ame, as_tibble(summary(margins(m_marginal))$AME))
  res_se <- bind_cols(res_se, as_tibble(summary(margins(m_marginal))$SE))
  res_p <- bind_cols(res_p, as_tibble(summary(margins(m_marginal))$p))
}

subscr_model <- tibble(term=res_ame$term)
subscr_model$ame <- apply(res_ame[,2:6],1, mean)
subscr_model$se <- apply(res_se[,2:6],1, mean)
subscr_model$p <- apply(res_p[,2:6],1, mean)

subscr_model <- summary(pool(pooled_subscr)) %>%
  dplyr::select(term, estimate, std.error, p.value) %>%
  left_join(., subscr_model)


# viewing
data.comp.view <- filter(data.comp, if_view==1)
data.comp.view.mids <- as.mids(data.comp.view)
pooled_view <- with(data.comp.view.mids, glm.nb(view_counts ~ gender + age + education + interest_politics +GovSymp  + timespan, 
                                                weight=weight))

## calculate AME for plot
for (i in 1:5)
{ 
  m_marginal <- glm.nb(view_counts ~ gender + age + education + interest_politics +GovSymp  + timespan, 
                       weight=weight, data=data.comp.view, subset=.imp==i)
  
  if (i==1)
  { 
    save_terms <- tibble(term=names(summary(margins(m_marginal))$AME))
    res_ame <- save_terms 
    res_se <- res_ame
    res_p <- res_ame
  }
  
  res_ame <- bind_cols(res_ame, as_tibble(summary(margins(m_marginal))$AME))
  res_se <- bind_cols(res_se, as_tibble(summary(margins(m_marginal))$SE))
  res_p <- bind_cols(res_p, as_tibble(summary(margins(m_marginal))$p))
}

view_model <- tibble(term=res_ame$term)
view_model$ame <- apply(res_ame[,2:6],1, mean)
view_model$se <- apply(res_se[,2:6],1, mean)
view_model$p <- apply(res_p[,2:6],1, mean)

view_model <- summary(pool(pooled_view)) %>%
  dplyr::select(term, estimate, std.error, p.value) %>%
  left_join(., view_model)
```

```{r, fig.height=10, fig.width=10}

# plot the AME values
margins <- view_model %>%
  bind_rows(., subscr_model) %>%
  bind_rows(., comment_model) %>%
  na.omit() %>%
  mutate(Type = case_when(
    row_number() <= 7 ~ 'View count',
    row_number() > 7 & row_number() <= 14 ~ 'Subscribe count',
    row_number() > 14 & row_number() <= 21 ~ 'Comment count'
  ))


labels <- rev(c("gender", "age", "education", "timespan", "interest in politcs", 
                "pro-gov",  "anti-gov"))

margins %>%
  mutate(Type = factor(Type, levels = c("View count", 
                                        "Subscribe count","Comment count"))) %>% 
  mutate(term = factor(term, levels = rev(c("gender","age","education","timespan","interest_politics",
                                            "GovSymp3","GovSymp1")))) %>% 
  ggplot(aes(term,ame,color=Type,fill=Type)) +
  geom_point(shape=21,size=3) +
  geom_pointrange(aes(ymin=ame-2*se, ymax=ame+2*se)) + 
  geom_hline(yintercept = 0,color="grey25",linetype="dashed") +
  theme_minimal() + 
  scale_fill_manual(values=c("#E07A5F","navyblue","#3D405B"))+
  scale_color_manual(values=c("#E07A5F","navyblue","#3D405B"))+
  coord_flip()+
  facet_wrap(~Type, scales="free", axis.labels="all_x")+
  scale_y_continuous(name="AME")+
  scale_x_discrete(name="",labels=labels)+
  theme(legend.position = "none")  +
  theme(axis.text=element_text(size=12), strip.text = element_text(
    size = 16))

# uncomment this block to save it
#ggsave("mi1_cor.png")
```
## AME with left/right as IVs

```{r}
# Comment 
pooled_comment <- with(data.comp.comment.mids, glm.nb(comment_counts ~ gender + age + education + interest_politics +LR  + timespan, 
                                                      weight=weight))
# calculate AME for plot
for (i in 1:5)
{ 
  m_marginal <- glm.nb(comment_counts ~ gender + age + education + interest_politics +LR  + timespan, 
                       weight=weight, data=data.comp.comment, subset=.imp==i)
  
  if (i==1)
  { 
    save_terms <- tibble(term=names(summary(margins(m_marginal))$AME))
    res_ame <- save_terms 
    res_se <- res_ame
    res_p <- res_ame
  }
  
  res_ame <- bind_cols(res_ame, as_tibble(summary(margins(m_marginal))$AME))
  res_se <- bind_cols(res_se, as_tibble(summary(margins(m_marginal))$SE))
  res_p <- bind_cols(res_p, as_tibble(summary(margins(m_marginal))$p))
}

comment_model <- tibble(term=res_ame$term)
comment_model$ame <- apply(res_ame[,2:6],1, mean)
comment_model$se <- apply(res_se[,2:6],1, mean)
comment_model$p <- apply(res_p[,2:6],1, mean)

comment_model <- summary(pool(pooled_comment)) %>%
  dplyr::select(term, estimate, std.error, p.value) %>%
  left_join(., comment_model)

# Subscription
pooled_subscr <- with(data.comp.subc.mids, glm.nb(subscribe_counts ~ gender + age + education + interest_politics +LR  + timespan, 
                                                  weight=weight))

## calculate AME for plot
for (i in 1:5)
{ 
  m_marginal <- glm.nb(subscribe_counts ~ gender + age + education + interest_politics +LR  + timespan, 
                       weight=weight, data=data.comp.subc, subset=.imp==i)
  
  if (i==1)
  { 
    save_terms <- tibble(term=names(summary(margins(m_marginal))$AME))
    res_ame <- save_terms 
    res_se <- res_ame
    res_p <- res_ame
  }
  
  res_ame <- bind_cols(res_ame, as_tibble(summary(margins(m_marginal))$AME))
  res_se <- bind_cols(res_se, as_tibble(summary(margins(m_marginal))$SE))
  res_p <- bind_cols(res_p, as_tibble(summary(margins(m_marginal))$p))
}

subscr_model <- tibble(term=res_ame$term)
subscr_model$ame <- apply(res_ame[,2:6],1, mean)
subscr_model$se <- apply(res_se[,2:6],1, mean)
subscr_model$p <- apply(res_p[,2:6],1, mean)

subscr_model <- summary(pool(pooled_subscr)) %>%
  dplyr::select(term, estimate, std.error, p.value) %>%
  left_join(., subscr_model)

# viewing
pooled_view <- with(data.comp.view.mids, glm.nb(view_counts ~ gender + age + education + interest_politics +LR  + timespan, 
                                                weight=weight))

# calculate AME for plot
for (i in 1:5)
{ 
  m_marginal <- glm.nb(view_counts ~ gender + age + education + interest_politics +LR  + timespan, 
                       weight=weight, data=data.comp.view, subset=.imp==i)
  
  if (i==1)
  { 
    save_terms <- tibble(term=names(summary(margins(m_marginal))$AME))
    res_ame <- save_terms 
    res_se <- res_ame
    res_p <- res_ame
  }
  
  res_ame <- bind_cols(res_ame, as_tibble(summary(margins(m_marginal))$AME))
  res_se <- bind_cols(res_se, as_tibble(summary(margins(m_marginal))$SE))
  res_p <- bind_cols(res_p, as_tibble(summary(margins(m_marginal))$p))
}

view_model <- tibble(term=res_ame$term)
view_model$ame <- apply(res_ame[,2:6],1, mean)
view_model$se <- apply(res_se[,2:6],1, mean)
view_model$p <- apply(res_p[,2:6],1, mean)

view_model <- summary(pool(pooled_view)) %>%
  dplyr::select(term, estimate, std.error, p.value) %>%
  left_join(., view_model)
```


```{r, fig.height=10, fig.width=10}

# plot the AME values
margins <- view_model %>%
  bind_rows(., subscr_model) %>%
  bind_rows(., comment_model) %>%
  na.omit() %>%
  mutate(Type = case_when(
    row_number() <= 7 ~ 'View count',
    row_number() > 7 & row_number() <= 14 ~ 'Subscribe count',
    row_number() > 14 & row_number() <= 21 ~ 'Comment count'
  ))


labels <- rev(c("gender", "age", "education", "timespan", "interest in politcs", 
                "left",  "right"))

margins %>%
  mutate(Type = factor(Type, levels = c("View count", 
                                        "Subscribe count","Comment count"))) %>% 
  mutate(term = factor(term, levels = rev(c("gender","age","education","timespan","interest_politics",
                                            "LR1","LR3")))) %>% 
  ggplot(aes(term,ame,color=Type,fill=Type)) +
  geom_point(shape=21,size=3) +
  geom_pointrange(aes(ymin=ame-2*se, ymax=ame+2*se)) + 
  geom_hline(yintercept = 0,color="grey25",linetype="dashed") +
  theme_minimal() + 
  scale_fill_manual(values=c("#E07A5F","navyblue","#3D405B"))+
  scale_color_manual(values=c("#E07A5F","navyblue","#3D405B"))+
  coord_flip()+
  facet_wrap(~Type, scales="free", axis.labels="all_x")+
  scale_y_continuous(name="AME")+
  scale_x_discrete(name="",labels=labels)+
  theme(legend.position = "none")  +
  theme(axis.text=element_text(size=12), strip.text = element_text(
    size = 16))

# uncomment this block to save it
ggsave("mi2_cor.png")
```

## Basic stats for DDPS - Table 9, 10

```{r}
load(paste(ROOTPATH, "data/youtube/yt_resplevel_data_1229.Rdata", sep=""))
data <- yt_resplevel  %>%
  dplyr::select(respondent_id, all_watch_sel, all_comment_sel, all_subscription)  %>%
  left_join(data, .)
data$agecat <-  sjmisc::rec(data$age, rec="1.6:3.4=1; 3.5:4.9=2; 5:6.4=3; 6.5:100=4")
```

```{r}
## print stats for Table 9
### viewing
print("all viewing")
data %>%
  filter(if_view==1) %>%
  descr(all_watch_sel, weights = weight)

data %>%
  filter(if_view == 1) %>%
  summarise(median = median(all_watch_sel, na.rm = TRUE)) # median

print("pol viewing")
data %>%
  filter(if_view==1) %>%
  descr(view_counts, weights = weight)

data %>%
  filter(if_view == 1) %>%
  summarise(median = median(view_counts, na.rm = TRUE)) # median

### subscribing
print("all subscribing")
data %>%
  tidyr::replace_na(list(all_subscription=0)) %>%
  descr(all_subscription, weights = weight)

data %>%
  tidyr::replace_na(list(all_subscription=0)) %>%
  summarise(median = median(all_subscription, na.rm = TRUE)) # median

print("pol subscribing")
data %>%
  tidyr::replace_na(list(all_subscription=0)) %>%
  descr(subscribe_counts, weights = weight)

data %>%
  tidyr::replace_na(list(all_subscription=0)) %>%
  summarise(median = median(subscribe_counts, na.rm = TRUE)) # median

### commenting
print("all commenting")
data %>%
  tidyr::replace_na(list(all_comment_sel=0)) %>%
  descr(all_comment_sel, weights = weight)

data %>%
  tidyr::replace_na(list(all_comment_sel=0)) %>%
  summarise(median = median(all_comment_sel, na.rm = TRUE)) # median

print("pol commenting")
data %>%
  tidyr::replace_na(list(comment_counts=0)) %>%
  descr(comment_counts, weights = weight)

data %>%
  tidyr::replace_na(list(comment_counts=0)) %>%
  summarise(median = median(comment_counts, na.rm = TRUE)) # median

### timespan
print("timespan")
data %>%
  tidyr::replace_na(list(all_watch_sel=0, all_comment_sel=0)) %>%
  mutate(no_ts=all_watch_sel+all_comment_sel) %>%
  subset(no_ts>0) %>%
  descr(timespan, weights = weight)

data %>%
  tidyr::replace_na(list(all_watch_sel=0, all_comment_sel=0)) %>%
  mutate(no_ts=all_watch_sel+all_comment_sel) %>%
  subset(no_ts>0) %>%
  summarise(median = median(timespan, na.rm = TRUE)) # median
```


```{r}
## print stats for Table 10

### viewing
data %>%
  subset(if_view==1) %>%
  group_by(gender) %>%
  summarise(s1=weighted_mean(all_watch_sel, weight), s2=weighted_se(all_watch_sel, weight))

data %>%
  subset(if_view==1) %>%
  group_by(agecat) %>%
  summarise(s1=weighted_mean(all_watch_sel, weight), s2=weighted_se(all_watch_sel, weight))

data %>%
  subset(if_view==1) %>%
  group_by(education) %>%
  summarise(s1=weighted_mean(all_watch_sel, weight), s2=weighted_se(all_watch_sel, weight))

### subscribing 
data %>%
  tidyr::replace_na(list(all_subscription=0)) %>%
  group_by(gender) %>%
  summarise(s1=weighted_mean(all_subscription, weight), s2=weighted_se(all_subscription, weight))

data %>%
  tidyr::replace_na(list(all_subscription=0)) %>%
  group_by(agecat) %>%
  summarise(s1=weighted_mean(all_subscription, weight), s2=weighted_se(all_subscription, weight))

data %>%
  tidyr::replace_na(list(all_subscription=0)) %>%
  group_by(education) %>%
  summarise(s1=weighted_mean(all_subscription, weight), s2=weighted_se(all_subscription, weight))

### commenting
data %>%
  tidyr::replace_na(list(all_comment_sel=0)) %>%
  group_by(gender) %>%
  summarise(s1=weighted_mean(all_comment_sel, weight), s2=weighted_se(all_comment_sel, weight))


data %>%
  tidyr::replace_na(list(all_comment_sel=0)) %>%
  group_by(agecat) %>%
  summarise(s1=weighted_mean(all_comment_sel, weight), s2=weighted_se(all_comment_sel, weight))

data %>%
  tidyr::replace_na(list(all_comment_sel=0)) %>%
  group_by(education) %>%
  summarise(s1=weighted_mean(all_comment_sel, weight), s2=weighted_se(all_comment_sel, weight))

### timespan
data %>%
  tidyr::replace_na(list(all_watch_sel=0, all_comment_sel=0)) %>%
  mutate(no_ts=all_watch_sel+all_comment_sel) %>%
  subset(no_ts>0) %>%
  group_by(gender) %>%
  summarise(s1=weighted_mean(timespan, weight), s2=weighted_se(timespan, weight))

data %>%
  tidyr::replace_na(list(all_watch_sel=0, all_comment_sel=0)) %>%
  mutate(no_ts=all_watch_sel+all_comment_sel) %>%
  subset(no_ts>0) %>%
  group_by(agecat) %>%
  summarise(s1=weighted_mean(timespan, weight), s2=weighted_se(timespan, weight))

data %>%
  tidyr::replace_na(list(all_watch_sel=0, all_comment_sel=0)) %>%
  mutate(no_ts=all_watch_sel+all_comment_sel) %>%
  subset(no_ts>0) %>%
  group_by(education) %>%
  summarise(s1=weighted_mean(timespan, weight), s2=weighted_se(timespan, weight))
```

```{r}
## print stats for Table 11

### viewing
data %>%
  subset(if_view==1) %>%
  group_by(gender) %>%
  summarise(s1=weighted_mean(view_counts, weight), s2=weighted_se(view_counts, weight))

data %>%
  subset(if_view==1) %>%
  group_by(agecat) %>%
  summarise(s1=weighted_mean(view_counts, weight), s2=weighted_se(view_counts, weight))

data %>%
  subset(if_view==1) %>%
  group_by(education) %>%
  summarise(s1=weighted_mean(view_counts, weight), s2=weighted_se(view_counts, weight))

### subscribing
data %>%
  tidyr::replace_na(list(subscribe_counts=0)) %>%
  group_by(gender) %>%
  summarise(s1=weighted_mean(subscribe_counts, weight), s2=weighted_se(subscribe_counts, weight))


data %>%
  tidyr::replace_na(list(subscribe_counts=0)) %>%
  group_by(agecat) %>%
  summarise(s1=weighted_mean(subscribe_counts, weight), s2=weighted_se(subscribe_counts, weight))

data %>%
  tidyr::replace_na(list(subscribe_counts=0)) %>%
  group_by(education) %>%
  summarise(s1=weighted_mean(subscribe_counts, weight), s2=weighted_se(subscribe_counts, weight))

### commenting
data %>%
  tidyr::replace_na(list(comment_counts=0)) %>%
  group_by(gender) %>%
  summarise(s1=weighted_mean(comment_counts, weight), s2=weighted_se(comment_counts, weight))


data %>%
  tidyr::replace_na(list(comment_counts=0)) %>%
  group_by(agecat) %>%
  summarise(s1=weighted_mean(comment_counts, weight), s2=weighted_se(comment_counts, weight))

data %>%
  tidyr::replace_na(list(comment_counts=0)) %>%
  group_by(education) %>%
  summarise(s1=weighted_mean(comment_counts, weight), s2=weighted_se(comment_counts, weight))
```


